An anthropological account of the Vim editor:\\ ouroboros, features and tweaks after 10 years of usage

### 2017-11-11 article/article.tex
ideas for enhancements

\noindent {\bf Potential enhancements} to this document are:
\begin{itemize}
  \item The inclusion of facilities such as reading emails and connecting over ssh.
    There is a working hack in~\cite{vimrc} for browsing over the WWW,
    but such aspect of Vim usage might receive more attention
    given that it is confortable to use the navigation and editing facilities
    and the resulting integrated environment.
  \item Updating of the information I can find about the issues discussed,
    such as about status lines in Section~\ref{visual1}.
  \item Include a discussion about Neovim.
    I have never used it, but it seems to be reaching a considerable user base
    and it might be feasable to give an account of Vim and Neovim
    after some tests and researching the official and user base documentation.
  \item Better cite documentation, plugins and Vim authors.
    I prefered to keep the references inline through \tttt{:h} commands
    and URLs, more in accordance with the style of Vim documentation,
    but bibliographical items constitute a valuable asset for academic literature,
    and some authors might find their work more pretiged if more
    thoroughly cited.
\end{itemize}

\noindent {\bf Potential next steps} in using Vim:
\begin{itemize}
  \item Measure the performance of text mining routines in Vim against those implemented in C or Python.
  \item Enhance the HTTP browsing capabilities of~\cite{vimrc}.
  \item Better integrate Python and Vimscript, especially for data visualization
    and syntax highlighting management.
    In accordance with the visualization issues described in
    Sections~\ref{visual1} and~\ref{visual2}.
  \item Make plugins for:
    \begin{itemize}
      \item listing all the mappings available in each mode and the typing combinations which are available
        for new mappings.
      \item Sessions, as described in Section~\ref{visual1}.
      \item AA messages (shouts): to keep track, document and share of working sessions
        as in~\cite{aa1,aa2}, with capabilities to manage AA sessions,
        send visual or sonic cues for temporal marks, use Vim state to build AA shouts,
        relate AA sessions to other media, such as software repositories,
        screencasts and images, interact with IRC channels and other social platforms.
      \item Slick Vim: a collection of the settings, mappings and plugins I use.
        Enhancements such as using \ttt{C-} commands also to browse tabs,
        shortcuts to join a window into a tab,
        and dummy minimal plugins as simplest, file type and syntax highlighting,
        Some more elaborate tweaks should also be present, such
        as breaking lines in sensible places for natural language texts
        while respecting e.g. \tttt{:se textwidth}.
      \item Dealing with .swo and .swp temporary files.
        In summary, if the restored .swo file has the same content
        and the file being opened,
        the restoration phase can be omitted.
        If the contents differ, Vim should open a tab with each file
        in a vertical split and run \tttt{:windo :diffthis}.
      \item Rendering images and equations.
        These are useful for using Vim in presentations
        or achieving a textual representation when it is mandatory,
        such as to comply with the limitations of a platform (e.g. Vim editor). 
        but also hold stylistic merits as ascii art is often
        very appreciated.
        One can both obtain an ascii representation of a binary image (e.g. JPG, PNG),
        and can directly render ascii charts from data using cues such are shape, position
        and color.
      \item Redirecting the commands that usually show the results in a 'more' interface,
        which cannot be searched nor copied,
        to a parsed and linked quickfix or location window.
        The basic idea is to use \tttt{:redir} command to redirect the output
        of such commands with \tttt{:se nomore}.
      \item Slide presentations. I've been using some automation for browsing
        slides and opening figures and some Vim users asked for the settings and
        commands. They are very elementary use of registers being executed over
        arbitrary but consistent textual patterns.
      \item Changing the color scheme an highlighting scheme incrementally
        and selectively using the features described in Section~\ref{visual2}.
    \end{itemize}
\end{itemize}

>>>>

\noindent {\bf Potential enhancements} to this document are:
\begin{itemize}
  \item The inclusion of facilities such as reading emails and connecting over ssh.
    There is a working hack in~\cite{vimrc} for browsing over the WWW,
    but such aspect of Vim usage might receive more attention
    given that it is confortable to use the navigation and editing facilities
    and the resulting integrated environment.
  \item Updating of the information I can find about the issues discussed,
    such as about status lines in Section~\ref{visual1}.
  \item Include a discussion about Neovim.
    I have never used it, but it seems to be reaching a considerable user base
    and it might be feasable to give an account of Vim and Neovim
    after some tests and researching the official and user base documentation.
  \item Better cite documentation, plugins and Vim authors.
    I prefered to keep the references inline through \tttt{:h} commands
    and URLs, more in accordance with the style of Vim documentation,
    but bibliographical items constitute a valuable asset for academic literature,
    and some authors might find their work more pretiged if more
    thoroughly cited.
  \item An analysis of my usage, e.g. according to \url{http://www.drbunsen.org/vim-croquet/}.
    This undertake might benefit from data from many users,
    which favors the potential plugin for usage analytics described in the next bullet list.
\end{itemize}

\noindent {\bf Potential next steps} in using Vim:
\begin{itemize}
  \item Measure the performance of text mining routines in Vim against those implemented in C or Python.
  \item Enhance the HTTP browsing capabilities of~\cite{vimrc}.
  \item Better integrate Python and Vimscript, especially for data visualization
    and syntax highlighting management.
    In accordance with the visualization issues described in
    Sections~\ref{visual1} and~\ref{visual2}.
  \item Make plugins for:
    \begin{itemize}
      \item listing all the mappings available in each mode and the typing combinations which are available
        for new mappings.
      \item Sessions, as described in Section~\ref{visual1}.
      \item AA messages (shouts): to keep track, document and share of working sessions
        as in~\cite{aa1,aa2}, with capabilities to manage AA sessions,
        send visual or sonic cues for temporal marks, use Vim state to build AA shouts,
        relate AA sessions to other media, such as software repositories,
        screencasts and images, interact with IRC channels and other social platforms.
      \item Slick Vim: a collection of the settings, mappings and plugins I use.
        Enhancements such as using \ttt{C-} commands also to browse tabs,
        shortcuts to join a window into a tab,
        and dummy minimal plugins as simplest, file type and syntax highlighting,
        Some more elaborate tweaks should also be present, such
        as breaking lines in sensible places for natural language texts
        while respecting e.g. \tttt{:se textwidth}.
      \item Dealing with .swo and .swp temporary files.
        In summary, if the restored .swo file has the same content
        and the file being opened,
        the restoration phase can be omitted.
        If the contents differ, Vim should open a tab with each file
        in a vertical split and run \tttt{:windo :diffthis}.
      \item Rendering images and equations.
        These are useful for using Vim in presentations
        or achieving a textual representation when it is mandatory,
        such as to comply with the limitations of a platform (e.g. Vim editor). 
        but also hold stylistic merits as ascii art is often
        very appreciated.
        One can both obtain an ascii representation of a binary image (e.g. JPG, PNG),
        and can directly render ascii charts from data using cues such are shape, position
        and color.
      \item Redirecting the commands that usually show the results in a 'more' interface,
        which cannot be searched nor copied,
        to a parsed and linked quickfix or location window.
        The basic idea is to use \tttt{:redir} command to redirect the output
        of such commands with \tttt{:se nomore}.
      \item Slide presentations. I've been using some automation for browsing
        slides and opening figures and some Vim users asked for the settings and
        commands. They are very elementary use of registers being executed over
        arbitrary but consistent textual patterns.
      \item Changing the color scheme an highlighting scheme incrementally
        and selectively using the features described in Section~\ref{visual2}.
      \item For bringing back all the splits after an \tttt{:only}.
        Also for bringing back the tabs after a \tttt{:tabo}.
      \item Run Python excepts from file in an IPython shell. 
        The buffer number of the terminal window should be stored,
        and than any selected lines should be run on that instance.
        Mappings should make available all movements to catch the excepts,
        execution of registers, remain on script or in the IPython shell.
        Also, terminal mode can use some improvements, such as \ttt{C-O} for
        one normal mode command.
      \item For keeping track of the usage and making analysis
        for optimizing the usage, as described in~\cite{http://www.drbunsen.org/vim-croquet/}. Usage analytics.
    \end{itemize}
\end{itemize}
